### 2017-05-10 paper/evaluation.tex
another pass

To answer \numRQSpeedupOne{}, we considered \numProjectsPar{} subjects from our
benchmark that use parallelization \emph{by default} when running
tests.  In those projects, parallelization is active without passing
any extra parameters.  Section~\ref{sec:rqC-1} describes in detail the
methodology we used to find these subjects.
%and
%Section~\ref{seq:rq6-tradeoffs}, we verified that both
%% executions produce the same outcome to eliminate noise from failing
%% tests.  To compute the speedup, we divide the time obtained in the
%% sequential execution by the time obtained from the default execution.
%% For instance, if a project runs the tests sequentially in $10m$ and
%% the same execution runs in $5m$ with parallelization enabled (default
%% execution), the speedup is two.

Figure~\ref{tab:speedup} summarizes results.  Lines are sorted by
abbreviated project names, which appear in bold.  Columns
``\emph{Group}'' and ``\emph{Name}'' indicate, respectively, the
project group and the name of the subject.  Column ``$T_s$'' shows
sequential execution time whereas column ``$T_p$'' shows parallel
execution time. Column ``$T_s/T_p$'' shows the speedup or slowdown
associated with parallel execution.   As usual, a ratio
above 1x denotes speedup and a ratio below 1x denotes slowdown.

\begin{figure}[h!]
\footnotesize
\centering
\resizebox{.45\textwidth}{!}{%
\begin{tabular}{llrrr}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & 
    \cellcolor{lightgray}1.01x\\%
Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
Long &\Comment{ Jenkins CI }Gerrit\Comment{ Plugin} & 51.19m & 40.31m &  1.26x\\%
Medium &\Comment{ Spotify }Helios& 4.46m & 1.63m & 2.73x\\%  
Medium &Javaslang& 2.18m & 1.82m & 1.19x\\%
Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m &
    \cellcolor{lightgray}9.2x\\%
Medium &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
\midrule
\textbf{average} &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\end{tabular}}
\caption{Speedup (or slowdown) of parallel execution ($T_p$) over
  sequential execution ($T_s$).  Default parallel configuration of
  Maven is used.  Abbreviation of project names appear in bold face
  and highest slowdown/speedup appear in gray color.}
\label{tab:speedup}
\end{figure}

@@

\begin{center}
\fbox{
  \begin{minipage}{8cm}
    \textit{Answering \numRQSpeedupOne{}:}~\emph{ The average speedup observed
      with default configurations of parallelization was
      \avgSpeedup{}x.}
  \end{minipage}
}
\end{center}

@@

\subsection{Threats to Validity}

\Fix{To appear... Elaborate CONSTRUCT, INTERNAL and EXTERNAL threats.
I'm going to be writing this ASAP as I finish to present the results
from RQ6}

\subsection{Lessons Learned}

\Fix{Marcelo can write this...}

>>>>

To answer \numRQSpeedupOne{}, we considered the \numProjectsPar{}
subjects from our benchmark that use parallelization \emph{by default}
(see Figure~\ref{tab:freqmodes-dynamic}).  We compared running times
with parallelization~---~configured by project owners~---~and without
parallelization.

%% In those projects, parallelization is active without
%% passing any extra parameters.  Section~\ref{sec:rqC-1} describes in
%% detail the methodology we used to find these subjects.
%and
%Section~\ref{seq:rq6-tradeoffs}, we verified that both
%% executions produce the same outcome to eliminate noise from failing
%% tests.  To compute the speedup, we divide the time obtained in the
%% sequential execution by the time obtained from the default execution.
%% For instance, if a project runs the tests sequentially in $10m$ and
%% the same execution runs in $5m$ with parallelization enabled (default
%% execution), the speedup is two.

Figure~\ref{tab:speedup} summarizes results.  Lines are sorted by
abbreviated project names.  Columns ``\emph{Group}'' and
``\emph{Name}'' indicate, respectively, the group and the name of the
subject.  Column ``$T_s$'' shows sequential execution time and column
``$T_p$'' shows parallel execution time. Column ``$T_s/T_p$'' shows
the speedup or slowdown.  As usual, a ratio above 1x denotes speedup
and a ratio below 1x denotes slowdown.

\begin{figure}[h!]
\centering
\resizebox{.45\textwidth}{!}{%
\scriptsize
\begin{tabular}{llrrr}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & 
    \cellcolor{lightgray}1.01x\\%
Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
Long &\Comment{ Jenkins CI }Gerrit\Comment{ Plugin} & 51.19m & 40.31m &  1.26x\\%
Medium &\Comment{ Spotify }Helios& 4.46m & 1.63m & 2.73x\\%  
Medium &Javaslang& 2.18m & 1.82m & 1.19x\\%
Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m &
    \cellcolor{lightgray}9.2x\\%
Medium &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
\midrule
\textbf{average} &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\end{tabular}}
\caption{Speedup (or slowdown) of parallel execution ($T_p$) over
  sequential execution ($T_s$).  Default parallel configuration of
  Maven is used.  Highest slowdown/speedup appears in gray color.}
\label{tab:speedup}
\end{figure}

@@

\begin{center}
\fbox{
  \begin{minipage}{8cm}
    \textit{Answering \numRQSpeedupOne{}:}~\emph{Considering the
      machine setup we used, the average speedup observed with default
      configurations of parallelization was \avgSpeedup{}x.}
  \end{minipage}
}
\end{center}

@@
